### 2017-11-14 README.Rmd
update README.
update instructions

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/everhartlab/sclerotinia-366/commits/master) [![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.1-brightgreen.svg)](https://cran.r-project.org/) [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)  [![Circle CI](https://circleci.com/gh/everhartlab/sclerotinia-366.svg?style=shield&circle-token=:circle-token)](https://circleci.com/gh/everhartlab/sclerotinia-366)

@@

# Citation

## Manuscript

@@

> Kamvar, Z. N., Amaradasa, B. S., Jhala, R., McCoy, S., Steadman, J., & Everhart, S. E. (2017, October 3). Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States. <http://doi.org/10.17605/OSF.IO/EJB5Y>

@@

 1. [table-1.md]
 1. [MCG-virulence.md]
 1. [locus-stats.md]
 1. [MLG-distribution.md]
 1. [mlg-mcg.md]
 1. [RDA-analysis.md]
 1. [pop-diff.md]
 1. [tree.md]
 1. [wmn-differentiation.md]
 1. [by-year.md]

# Reproducing the analysis

## Docker

This repository contains a [Dockerfile](Dockerfile), which specifies the
instructions to build a [docker](https://www.docker.com/) container. This is
designed to capture the complete development environment of the analysis so
that it can be accurately reproduced. The image is ~2.71Gb, so be sure that you
have enough memory on your computer to run it.

@@

> Note: both ways assume that you are in the analysis directory

@@

```
docker run --rm -dp 8787:8787 zkamvar/sclerotinia-366:latest
```

This will spin up the Docker container on your machine and expose it to port 8787. You can open your browser and type `localhost:8787`, and an instance of Rstudio server will appear. Sign in with the username: rstudio and password: rstudio.

@@

From here you can re-run the analyses to your heart's content.

@@

If you don't want to pull from docker hub, you can build the container.

```sh
docker build -t sclerotinia-366 .
```

@@

[Makefile]: Makefile
[table-1.md]: results/table-1.md
[MCG-virulence.md]: results/MCG-virulence.md
[locus-stats.md]: results/locus-stats.md
[MLG-distribution.md]: results/MLG-distribution.md
[mlg-mcg.md]: results/mlg-mcg.md
[RDA-analysis.md]: results/RDA-analysis.md
[pop-diff.md]: results/pop-diff.md
[tree.md]: results/tree.md
[wmn-differentiation.md]: results/wmn-differentiation.md
[by-year.md]: results/by-year.md

>>>>

[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-2F4096.svg)](https://github.com/everhartlab/sclerotinia-366/commits/master) 
[![Licence](https://img.shields.io/badge/license-MIT%20License-2F4096.svg)](http://choosealicense.com/licenses/mit/)  
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.2-2F4096.svg)](https://cran.r-project.org/) 
[![Circle CI](https://circleci.com/gh/everhartlab/sclerotinia-366.svg?style=shield&circle-token=:circle-token)](https://circleci.com/gh/everhartlab/sclerotinia-366)

@@

# Citations

## Preprint

@@

> Kamvar, Z. N., Amaradasa, B. S., Jhala, R., McCoy, S., Steadman, J. R., & Everhart, S. E. (2017, November). Data and analysis for population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States. <http://doi.org/10.17605/OSF.IO/EJB5Y>

@@

 1. [table-1.md]
 1. [MCG-virulence.md]
 1. [locus-stats.md]
 1. [MLG-distribution.md]
 1. [mlg-mcg.md]
 1. [RDA-analysis.md]
 1. [pop-diff.md]
 1. [tree.md]
 1. [wmn-differentiation.md]
 1. [by-year.md]
 1. [compare-aldrich-wolfe.md]

# Analysis

## Background

The analysis is controlled via two docker containers:

 1. [sclerotinia-366-dependencies](https://hub.docker.com/r/zkamvar/sclerotinia-366-dependencies/): defines the complete software environment used, built on top of the [rocker/verse:3.4.2](https://hub.docker.com/r/rocker/verse) container. **(See the [Dockerfile](https://osf.io/mwv6d/))**
 2. [sclerotinia-366](https://hub.docker.com/r/zkamvar/sclerotinia-366/) is built on top of the above container and contains the results of the analysis. **(See the [Dockerfile](https://osf.io/tvfju/))**

The `sclerotinia-366-dependencies` container is regularly rebuilt on docker hub whenever `rocker/verse:3.4.2` updates and the `sclerotinia-366` container is rebuilt on [CircleCI](https://circleci.com/gh/everhartlab/sclerotinia-366) whenever the git repository is updated.

As of this writing, the containers are up to date with R version 3.4.2 and packages downloaded from the [MRAN snapshot on 2017-10-31](https://mran.microsoft.com/snapshot/2017-10-31/).

Jump to [Reproduction via Docker](#reproduction-via-docker) or [Reproduction Locally](#locally).

------

## Reproduction via Docker

This repository contains a [Dockerfile](Dockerfile), which specifies the
instructions to build a [docker](https://www.docker.com/) container. This is
designed to capture the complete development environment of the analysis so
that it can be accurately reproduced. The image is ~3.21Gb, so be sure that you
have enough memory on your computer to run it.

@@

@@

To run the docker container, make sure you have Docker running, open your terminal and type:

```bash
docker run --name ssc --rm -dp 8787:8787 -e ROOT=TRUE zkamvar/sclerotinia-366:latest
```

This will first check to make sure you have the container on your machine. If you don't, Docker will automatically download it for you. It will spin up the Docker container on your machine, give it the name "ssc", and expose it to port 8787. You can open your browser and type `localhost:8787`, and an instance of Rstudio server will appear. Sign in with the following credentials:

 - username: rstudio 
 - password: rstudio.

@@

From here you can re-run the analyses to your heart's content. 
**Don't forget to stop the container when you are finished:**

```bash
docker stop ssc
```

@@

If you don't want to pull from docker hub, you can build the container locally.
First, download the repository

```bash
git clone https://github.com/everhartlab/sclerotinia-366.git
cd sclerotinia-366/
docker build -t sclerotinia-366 .
```

@@

> Note: This analysis is only guaranteed to work with [the stated software environment](#packages-used).

[Makefile]: Makefile
[table-1.md]: results/table-1.md
[MCG-virulence.md]: results/MCG-virulence.md
[locus-stats.md]: results/locus-stats.md
[MLG-distribution.md]: results/MLG-distribution.md
[mlg-mcg.md]: results/mlg-mcg.md
[RDA-analysis.md]: results/RDA-analysis.md
[pop-diff.md]: results/pop-diff.md
[tree.md]: results/tree.md
[wmn-differentiation.md]: results/wmn-differentiation.md
[by-year.md]: results/by-year.md
[compare-aldrich-wolfe.md]: results/compare-aldrich-wolfe.md
